Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-09-01 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
say model is 2D x-z slice, no Coriolis

\section{Model}
\label{sec:model}
\TODO{Use model in 2D x-z slice configuration without Coriolis forces}
\TODO{Add info about the different numerical options that are assessed in combination with the orography treatment}

@@

The model uses C-grid staggering in the horizontal and Lorenz staggering in the vertical such that $\theta$, $\rho$ and $\Pi$ are stored at cell centres and the covariant component of velocity at cell faces.
A minor change has been made to the non-orthogonal formulation as described in \citet{weller-shahrokhi2014} to improve stability on non-orthogonal grid, and this is detailed in appendix A.

>>>>

\section{Model}
\label{sec:model}
\TODO{Add info about the different numerical options that are assessed in combination with the orography treatment}

@@

The model is operated in a two-dimensional $x$--$z$ slice configuration without Coriolis forces.  The model uses the C-grid staggering in the horizontal and the Lorenz staggering in the vertical such that $\theta$, $\rho$ and $\Pi$ are stored at cell centres and the covariant component of velocity at cell faces.
A minor change has been made to the non-orthogonal formulation as described in \citet{weller-shahrokhi2014} to improve stability on non-orthogonal grid, and this is detailed in appendix A.
